Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-26 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Made the section H2 instead of H3
Separated the multiple countries entry into single rows

### Validation methods

@@

### Connection of authors to the studied locations 
```{r}
author_connectedness_to_location_fmd <- fmd_data %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(!country_studied %in% c('none', 'west_africa', 'global', 
                                 'northern_hemisphere', 'southeast_asia',
                                 'who_southeast_asia_region')) %>% 
  group_by(collab_type) %>% 
  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  arrange(collab_type, desc(yes)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no')) %>% 
  ungroup()

>>>>

@@

### Connection of authors to the studied locations 
```{r}
author_connectedness_to_location_fmd <- fmd_data %>% 
  filter(author_in_country_studied != 'not_applicable') %>% 
  filter(!country_studied %in% c('none', 'west_africa', 'global', 
                                 'northern_hemisphere', 'southeast_asia',
                                 'who_southeast_asia_region')) %>% 
  separate_rows(country_studied,  sep = ' ') %>% 
  group_by(collab_type) %>% 
  count(country_studied, author_in_country_studied, sort = TRUE) %>% 
  pivot_wider(names_from = author_in_country_studied, values_from = n) %>% 
  replace_na(list(yes = 0, no = 0)) %>% 
  arrange(collab_type, desc(yes)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('yes', 'no')) %>% 
  adorn_pct_formatting(... = c('yes', 'no')) %>% 
  adorn_ns(... = c('yes', 'no')) %>% 
  ungroup()
